---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cbsafinder

## Overview

The goal of cbsafinder is finding the CBSA of US addresses, using the census and Google geocoding APIs. CBSAs are core based statistical areas; they represent one or more counties tied to an urban center of a given size. CBSAs are often used in the retail and real estate industries to help determine the geographic area of a given address. 

## Installation

Install the development version of the package from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("WarbyParker/cbsafinder")
```

## Getting Started

First, start by loading the package. The core function in cbsafinder looks up the CBSA (and a few other bits of handy info) given a U.S. address. So let's say that you want to know the CBSA of the giant Hollywood sign in California. Pass the address as a string to geocode_address() and voila! The Hollywood sign is in Los Angeles-Long Beach-Anaheim, CA.  

```{r example}
library(cbsafinder)
geocode_address("4059 Mount Lee Drive, Hollywood, CA 90068")
```

If you only know part of the address or forget to enter some info, the function still works! 

```{r}
geocode_address("4059 Mount Lee Drive")
```

Just be sure to pass the address as a string (i.e. remember your ""), or the function will fail.  

```{r error = TRUE}
geocode_address(4059 Mount Lee Drive, Hollywood, CA 90068)
```

Also, ``geocode_address()`` takes one address as an argument and no more, so something like this will also fail.  

```{r error = TRUE}
geocode_address(c("4059 Mount Lee Drive, Hollywood, CA 90068", "The White House, 1600 Pennsylvania Avenue NW, Washington, DC 20500"))
```

But purrr's map family of functions comes in handy for passing multiple addresses at once. Here we use ``purrr::map_df()`` to return a user friendly output. 

```{r}
my_addresses <- c("4059 Mount Lee Drive, Hollywood, CA 90068", "The White House, 1600 Pennsylvania Avenue NW, Washington, DC 20500")

purrr::map_df(my_addresses, ~cbsafinder::geocode_address(.x))
```


## Where to Find Help

If you find a bug, please file a reproducible example on [GitHub](https://github.com/WarbyParker/cbsafinder/issues).
